### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revise Introduction

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009, ``cryptocurrencies have emerged as the first generation of blockchain technology'' \cite{alharby_blockchain_2017}. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation \cite{alharby_blockchain_2017}, aim to provide a platform for building more sophisticated and complex applications on top of the technology. These are built with smart contracts, programs written in Turing-complete languages. Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{chen_under-optimized_2020}. This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations. Not only can such applications generate unsustainable costs when executed on the blockchain, but may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording \cite{thiemann_2020}. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage. Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself (cf. NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input. \\
Consider, for instance, the following smart contract:
\begin{lstlisting}[caption=Smart contract expecting a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
The assumption, that the given integer $p$ is a prime, can be expressed as an explicit assertion in predicate logic \cite{thiemann_2020}: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop. Assuming computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example is a contract that expects an array of integers sorted in ascending order:

\begin{lstlisting}[caption=Smart contract expecting a sorted array \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
contract Sorted {
  function find ( int [50] a , int v ) public {
    // assume a is sorted
  }
}
\end{lstlisting}

The assumption that the list is sorted, expressed in predicate logic, is
\begin{equation}\label{eq:sorted}
	(\forall n) (0 \leq n < |a| - 1) \Rightarrow a[n] \leq a[n+1]
\end{equation}

@@

\section{Objective}
This thesis proposes the portrayed approach of a distributed assertion checking scheme in order to make more efficent use of off-chain resources. The realisation of such assertions consists of two components - the off-chain design and implementation of supporting infrastructure, as well as the extension of the smart contract language and amendment of the blockchain protocol, s.t. these assertions are triggered and handled correctly by the network. The focus of this thesis is put primarily on the off-chain component and the development of a toolchain that transforms and translates assertions to executable code for the target platform, but elaborates on the protocol design where necessary. To this end, a first approximation of a set of formulas amenable for distributed assertion checking is defined, special cases are identified and, if necessary, excluded. While the off-chain design and toolchain should be partially applicable to any blockchain supporting smart contracts, the case example for the protocol-specific parts of the design targets the Tezos blockchain and its built-in contract language Michelson. On the basis of the chosen design, the thesis evaluates the efficiency of the approach in terms of costs incurred by checking a formula on Tezos, and discusses if, and under which conditions, these costs are competitive versus a local approach.

>>>>

\chapter{Introduction}\label{chap:introduction}
Headed by Bitcoin in 2009 \cite{bitcoin-whitepaper}, the first generation of blockchain technology emerged in form of cryptocurrencies. However, their transactions are mostly limited to simple monetary transactions or registration of assets or ownerships \cite{alharby_blockchain_2017}. More recent blockchains, considered as the second generation, aim to provide a platform for building more sophisticated and complex applications on top of the technology. Some prominent examples for such blockchains are Ethereum \cite{eth-whitepaper}, Tezos \cite{goodman_tezos_2014} or Cardano \cite{cardano_essay}, which plans to introduce smart contracts in an update this year \cite{cardano_alonzo}. Blockchain-based applications are built with smart contracts, programs written in Turing-complete languages. Running a smart contract, though, generates costs proportional to the amount and complexity of computations, as well as its storage usage \cite{alharby_blockchain_2017}. These fees, often measured in a unit called ``gas'', have to be paid for by the user in order to compensate the miners for their efforts \cite{narayanan_bitcoin}. This creates a powerful incentive to keep smart contracts simple and efficient, while in reality, meaningful applications still might need to perform some resource intensive computations. Not only can such applications generate unsustainable costs when executed on the blockchain, but may also reach gas limits imposed by the blockchain's protocol. \\
In order to avoid these costs and restrictions, such an application could perform some computations outside of the blockchain context (i.e., off-chain) and only submit the results to a smart contract as an input parameter for further processing or recording. By trusting that the submitted results are correct, this approach raises both safety and security issues. Invalid results can be submitted unintentionally as a result of a wrong computation, or a third party may pass them intentionally to cause harm or take advantage. Consequently, submitted parameters should be checked for assumed properties before the smart contract is executed. Although in many cases, verifying a solution takes less time than computing the result itself (cf. NP-hard problems \cite{nph_problems} or sorting algorithms \cite{review_sorting}\cite{cpp_issorted}), the generated costs for checking the validity increase with the size of the input. \\
Consider the smart contract \texttt{Example}, which is shown in \lstref{lst:prime} and features a function \texttt{f}. The function takes an input value \texttt{p} of type integer and should make use of the assumption that \texttt{p} is a prime number.
\begin{lstlisting}[caption=Smart contract with a function that expects a prime number \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:prime]
contract Example {
	function f ( int p ) public {
	// assume p is prime
	...
	}
}
\end{lstlisting}
This assumption ``$p$ is a prime number'' can be expressed with the following explicit assertion in predicate logic: 
\begin{equation}\label{eq:prime}
    (\forall n) (2 \le n \le \sqrt{p}) \Rightarrow (p \% n) \neq 0
\end{equation}
To check whether this property holds for $p$, the contract has to execute a loop over the range $[2, \sqrt{p}]$. Assuming that computing the body of the loop takes constant time, this test has a time complexity of $\mathcal{O}(\sqrt{p})$ and therefore generates costs linear in $\sqrt{p}$ on top of the cost for executing the actual contract. Thus, a mechanism is required that allows the smart contract to make use of the result computed by an off-chain source, without having to check its validity locally with scaling costs.

@@

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Function \texttt{find} of contract \texttt{Sorted}, shown in \lstref{lst:sorted}, expects a statically sized array of integers and a single integer value. In order to find the value \texttt{v} in \texttt{a} more efficiently, the array is assumed to be sorted.

\begin{lstlisting}[caption=Smart contract expecting a sorted array \cite{thiemann_2020}, numbers=none, language=Solidity, label=lst:sorted]
contract Sorted {
  function find ( int [50] a , int v ) public {
    // assume a is sorted
    ...
  }
}
\end{lstlisting}

The explicit assertion of this assumption (in the variant of an ascending sorting) can be expressed as follows in predicate logic:
\begin{equation}\label{eq:sorted}
	(\forall n) (0 \leq n < |a| - 1) \Rightarrow a[n] \leq a[n+1]
\end{equation}

@@

\section{Objective}
This thesis proposes a model for the portrayed approach of a distributed assertion checking scheme, to make more efficient use of off-chain computations. In this model, results of such computations are validated on-chain by the validators of the network. In order to do so, they invoke assertion smart contracts which point-wise check whether the result satisfies certain properties. When claiming an assertion failure, a validator publishes a counterexample to be scrutinized by the other validators. If they come to a consensus about the invalidity, the result is rejected. Provided that the assertion is cheaper than the computation itself, the purpose of this proposal is not only to reduce financial costs for the users, but also to overcome limitations in scalability.

The realisation of such assertions consists of an off-chain and an on-chain component. The off-chain component is a toolchain to specify, integrate and generate assertion contracts that can be deployed to the blockchain. It defines of a domain-specific language which allows developers to specify assertions for each entrypoint of a Smart Contract. The toolchain implements a pipeline which transforms the assertion, links it with the Smart Contract and translates it to the Smart Contract language. \\
The on-chain component consists of an amendment of the blockchain protocol to include transactions that can trigger the distributed execution of assertions and implement a consensus mechanism for counterexamples.

The focus of this thesis is put primarily on the off-chain component, but it elaborates on the protocol design where necessary.  Even though efforts were made to keep the design as generic and re-usable as possible, the implementation targets the Tezos blockchain and its built-in contract language Michelson. On the basis of the design and implementation for Tezos, the thesis evaluates the efficiency and incurred costs of this approach and discusses whether, and under which conditions, they can be competitive versus a centralized assertion approach.

\section{Related work}

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Revise Introduction

\section{Cost analysis}\label{sec:usecase_cost}
For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of executing a contract on the blockchain that centrally checks a formula. Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas. The following is thus based on the gas model of Tezos \cite{morley_gasmodel}\cite{tezos_repo}, which is described in more detail in \secref{sec:tezos}. According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ calling a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
\begin{align}\label{eq:gas_transaction}
\begin{split}
GasConsumed(T) = \quad &base \, amount \\
+& \, gasRead(code) \\
+& \, gasRead(storage) \\
+& \, gasDeserialize(storage, \, arg) \\
+& \, gasParseType(parameter \, type, \, storage) \\
+& \, gasParseData(storage, \, arg) \\
+& \, gasParseCode(code) \\
+& \, gasInterpret(code, \, arg, \, storage) \\
+& \, gasUnparse(storage) \\
+& \, gasSerialize(storage) \\
+& \, gasWrite(storage) \\
+& \, \sum_{i \in I} GasConsumed(i)
\end{split}
\end{align}
Assuming that the storage of the contract is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remains constant for each $T$. The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}. \\
Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$. Contract \texttt{Foo} takes an integer, whose byte sequence representation does not increase significantly with higher values. Thus, the increase in overall costs is mainly accounted for by the interpretation. Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which causes noticeably higher deserialization and parsing costs with increasing input sizes. 
\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
contract Foo {
  function foo (int a) public {
    for (uint i = 0; i < a; i++) {
      assert(a == a)
    }
  }
}
\end{lstlisting}
\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract iterating over a list]
contract Bar {
  function bar (int [] b) public {
    for (uint i = 0; i < b.length; i++) {
      assert(b[i] = b[i])
    }
  }
}
\end{lstlisting}

\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling the dummy contracts on the Delphinet test network running the protocol 007 Delphi \cite{tezos_docs}. As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.

\begin{figure}[p]
\centering
\includegraphics[width=0.9\linewidth]{figures/2-use_cases/cost_analysis}
\caption{Gas consumption of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
\label{fig:use_case_cost}
\vspace{128in}
\end{figure}

A repeated cost analysis is carried out in \secref{sec:cost_analysis_distributed} in order to assess whether, or how, distributed assertion checking, as described in the following chapters, can achieve a reduction of these costs.

>>>>

\section{Cost analysis}\label{sec:usecase_cost}
For the purpose of having a benchmark for the evaluation of the distributed approach, this section analyses the cost of executing a contract on the blockchain that centrally checks a formula. Given that the target blockchain is Tezos, the computational and storage-related costs of a transaction are represented in units of gas. Although they are not paid directly in terms of fees, the actual fees paid to the miner (called bakers in Tezos) are based on the gas consumption \cite{tezos_docs}. The gas model of Tezos is described in more detail in \secref{sec:tezos}. According to this model, the total gas consumption of a transaction $T(source,\, destination=C,\, arg, \, ...)$ calling a smart contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}, where $I$ is the set of internal operations:
\begin{align}\label{eq:gas_transaction}
\begin{split}
GasConsumed(T) = \quad &base \, gas \, cost \\
+& \, gasRead(code) \\
+& \, gasRead(storage) \\
+& \, gasDeserialize(storage, \, arg) \\
+& \, gasParseType(parameter \, type, \, storage) \\
+& \, gasParseData(storage, \, arg) \\
+& \, gasParseCode(code) \\
+& \, gasInterpret(code, \, arg, \, storage) \\
+& \, gasUnparse(storage) \\
+& \, gasSerialize(storage) \\
+& \, gasWrite(storage) \\
+& \, \sum_{i \in I} GasConsumed(i)
\end{split}
\end{align}
Assuming that the storage of the contract is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remains constant for each $T$. The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow monotonically with increasing sizes of $arg$ \cite{morley_gasmodel}\cite{tezos_repo}. \\
Consider the following simple contracts --- they do not do anything useful, but can be used to approximate the amplification of costs with regard to $arg$. Contract \texttt{Foo} takes an integer, whose byte sequence representation does not increase significantly with higher values. Thus, the increase in overall costs is mainly accounted for by the interpretation. Contract \texttt{Bar}, on the other hand, executes similar operations but expects a list of integers, which additionally causes higher deserialization and parsing costs with increasing input sizes. 
\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract executing a loop]
contract Foo {
  function foo (int a) public {
    for (uint i = 0; i < a; i++) {
      assert(a == a)
    }
  }
}
\end{lstlisting}
\begin{lstlisting}[numbers=none, language=Solidity, caption=Simple dummy contract iterating over a list]
contract Bar {
  function bar (int [] b) public {
    for (uint i = 0; i < b.length; i++) {
      assert(b[i] = b[i])
    }
  }
}
\end{lstlisting}

\figref{fig:use_case_cost} shows the reported gas consumption of transactions calling corresponding dummy contracts in Michelson (cf. Appendix \ref{apx:cost_analysis_contract}) on the Delphinet test network, running the protocol 007 Delphi \cite{tezos_docs}. As to be expected, the gradient of the cost function in the case of \texttt{Bar} is higher due to additional serialization and parsing costs, namely $\frac{dx}{dy} = 16$ compared to $\frac{dx}{dy} = 6$ for \texttt{Foo}.
\begin{figure}[p]
\centering
\includegraphics[width=0.9\linewidth]{figures/2-use_cases/cost_analysis}
\caption{Gas consumption of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
\label{fig:use_case_cost}
\vspace{128in}
\end{figure}

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Revise Introduction

\chapter{Generic Off-Chain Design}\label{chap:offline}
The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure. The previous chapter defined a formal set of logical formulae amenable for this approach and gave some in-depth examples. As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
The purpose of the off-chain infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain. Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way. This chapter describes the generic part of the off-chain design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}. As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples. The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}. Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and the cost incurred by increasing it.

\section{Assertion syntax}\label{sec:syntax}
The assertion syntax is described in two versions by the EBNF grammars shown in appendix \ref{apx:grammar}. One version implements a prefix and the other one an infix notation. The pipeline currently supports the prefix notation with mandatory parentheses to avoid the need of handling operator precedences. To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and thereby also Michelson.\\
A file containing assertions (henceforth referred to as ``assertion contract'') contains at least one assertion for some function or entrypoint of the original contract (henceforth referred to as ``parent contract''). An assertion begins with a signature consisting of an optional tag followed by a parameter type declaration. The tag can be used for documentation, but may sometimes be needed to indicate to which function of the parent contract the assertion should be assigned. The body is an (optional) nesting of quantifiers and conditions around exactly one assertion. Conditionals can be used to restrict the quantification domains or for some other constraints. For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it. \\
In order to make the frontend generic, the assertion grammar constitutes a union of operations and types for the target languages. This also allows the transformation to be oblivious of the target platform and be identical for all backends. The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides ( \secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this). Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.\\

As an example, consider a variation of the formula given in \eqref{eq:sorted} that checks whether a given list is sorted in ascending order:
\begin{equation}\label{eq:sorted_v2}
	(\forall n : int)(\forall m : int) (0 \leq n < m < |a|) \Rightarrow a[n] \leq a[m]
\end{equation}
The respective assertion that checks this property for the parent contract from \lstref{lst:sorted} could be expressed as follows:
\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}

@@

\section{Frontend of the pipeline}\label{sec:pipeline_front}
The frontend of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation. These stages are generic and independent of the target platform and produce an abstract syntax tree (AST) of the assertion that is passed to the respective back-end through a public interface.
\begin{figure}[h]
\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
\caption{The stages of the generic frontend of the compilation pipeline}
\label{fig:pipeline_frontend}
\end{figure}
OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain refer to \secref{sec:tezos}). This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries. \chapref{chap:offline_tezos} goes into more details about this.

>>>>

\chapter{Generic Off-Chain Design}\label{chap:offline}
The implementation of distributed assertion checking on any blockchain requires some off-chain considerations and infrastructure. The previous chapter defined a formal set of logical formulas amenable for this approach and gave some in-depth examples. As stated before, the proposed implementation in the following chapters is, for the most part, restricted to formulas of predicate logic using universal quantification.\\
The purpose of the off-chain infrastructure is to provide a syntax for stating assertions that check logical formulas, as well as a toolchain to compile these assertions into code that can be originated on the target blockchain. Depending on the individual solution for the respective blockchain protocol, this can either be the original contract extended directly with the assertion code, or as a separate contract that extends the original contract in some other way. This chapter describes the generic part of the off-chain design, which corresponds to the frontend of the compilation pipeline shown in \figref{fig:pipeline_frontend}. As a start, \secref{sec:syntax} describes the concrete syntax for writing assertions and shows how it expresses some of the previously given examples. The stages of the pipeline frontend, including parsing and transforming the original assertions to assertions that check for counterexamples, are described in \secref{sec:pipeline_front}. Lastly, \secref{sec:accuracy} analyses the reliability of distributed assertion checking as proposed and to what extent it affects the costs.

% provide a high level language specifying complex computations that way  is  hard  and  inconvenient
% 1) propose a model/approach to make use of off-chain computations that can be verified with explicit assertions
% 2) contribute a toolchain that consists of a domain-specific language and a compilation pipeline that generates assertion smart contracts for the target blockchain Tezos. efforts were made to keep this as generic as possible, s.t. it can be extended for other target platforms as well
% extend smart contracts and the VM with opcodes

\section{Assertion syntax}\label{sec:syntax}
The assertion syntax is described in two versions by the grammars in extended Backus-Naur form (EBNF) shown in appendix \ref{apx:grammar}. One version implements a prefix and the other one an infix notation. The pipeline currently supports the prefix notation with mandatory parentheses to avoid the need of handling operator precedences. To avoid context switches (at least for developers on Tezos), the assertion syntax references those of OCaml and thereby also Michelson.\\
\lstinputlisting[caption=Assertion contract for checking if a list is sorted, language=Assertion, label={lst:sorted_assertion}]{listings/sorted.tza}
A file containing assertions (henceforth referred to as ``assertion contract'') contains at least one assertion for some function or entrypoint of the original contract (henceforth referred to as ``parent contract''). An assertion begins with a signature consisting of an optional tag denoted by \%, followed by a parameter pattern. The tag can be used for documentation purposes, but may sometimes be needed to indicate which function of the parent contract the assertion should be assigned to by mirroring the entrypoint name. Parameter patterns are similar to patterns in OCaml --- they are templates that match shapes of data structures and binds identifiers to the components of them. The pattern given in the signature must match the parameter type of the entrypoint it refers to. The body is an (optional) nesting of quantifiers and conditions around exactly one assertion. Conditionals can be used to restrict the quantification domains or for some other constraints. For completeness, the existential quantifier is already included in the grammar, however the current version of the pipeline will reject any assertions containing it. \\
In order to make the frontend generic, the assertion grammar constitutes a union of operations and types for the target languages. This also allows the transformation to be oblivious of the target platform and be identical for all backends. The current version of the grammar recognizes all types present in the Tezos VM and a subset of operations that Michelson provides (\secref{sec:tezos} contains an introduction to Tezos and Michelson and goes more into detail about this). Responsible for rejecting any assertions containing unsupported types or operations are the respective backends.\\

As an example, consider a variation of the formula given in \eqref{eq:sorted} that checks whether a given list is sorted in ascending order:
\begin{equation}\label{eq:sorted_v2}
	(\forall n : int)(\forall m : int) (0 \leq n < m < |a|) \Rightarrow a[n] \leq a[m]
\end{equation}
The respective assertion that checks this property for the parent contract, given in \lstref{lst:sorted}, is expressed in \lstref{lst:sorted_assertion}.

@@

\section{Frontend of the pipeline}\label{sec:pipeline_front}
The frontend of the compilation pipeline comprises of a command-line interface (CLI), a parser and the transformation. These stages are generic and independent of the target platform, and produce an abstract syntax tree (AST) of the assertion. This AST	is then passed to the respective back-end through a public interface.
\begin{figure}[h]
\includegraphics[width=\linewidth]{figures/3-offline/pipeline_frontend}
\caption{The stages of the generic frontend of the compilation pipeline}
\label{fig:pipeline_frontend}
\end{figure}
OCaml was chosen as a programming language to implement the pipeline, given that it's also used to develop the Tezos blockchain. This avoids context switches within the Tezos eco-system and allows to build on top of the Tezos libraries (cf. \secref{sec:tezos}).

### 2021-04-15 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Revision Chapter 2
Revise Introduction

>>>>

\todo{Cheaper for the network if not all validators have to execute the whole local check! however, placing these costs on the users will cause them to use the local approach -> users need incentives to use it too! -> blockchain protocol could/should solve this! (e.g. use rewards instead of costs)}
\todo{Every transaction is processed at every node in the network,which limits throughput}
